Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-29 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Correct AUDPC calculation in Premer

Premer_13_dat <- cbind(Premer_13_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Premer_13[,c("Inc_31D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
                                                     Premer_13_dat$planting_date[1],
                                                  12+19)
                                        )
                          )

>>>>

Premer_13_dat <- cbind(Premer_13_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Premer_13[,c("Inc_31D")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Premer_13_dat$first_sign_disease[1]-7)-
                                                     as.Date("2013-01-28", format = "%Y-%m-%d"),
                                                  12+19)
                                        )
                          )
